---
title: "Group 11 presentation"
# subtitle: "MiRNA expression in squamous cell carcinoma and adenocarcinoma of the esophagus and associations with survival"
author: "Dalsberg Jørgensen, Jonas; Gutierrez Leon, Alvaro; Hoang Viet Minh Pham, Jake; Romero Yianni, Daniel"
date: "5/7/2022"
output:
  ioslides_presentation:
    #widescreen: true
    #smaller: true
---
<style type="text/css">
body p {
  color: #000000;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DiagrammeR)
```

## Introduction
- **Dataset source:** MiRNA expression in squamous cell carcinoma and adenocarcinoma of the esophagus and associations with survival.

<br>

- **Objective of the project:** To reproduce the findings of the authors and elaborate on their visualizations.

## Materials and Methods
### Patient data: 
- **GSE13937_series_matrix.txt**
<br>

- National Center for Biotechnology Information website   (https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE13937)

<br>

### Microarray information:
- **A-GEOD-8835.adf.txt** and **A-GEOD-8835_comments.txt** 

- European Bioinformatics Institute website (https://www.ebi.ac.uk/arrayexpress/arrays/A-GEOD-8835/)  


## Materials and Methods
### Flowchart of the wrangling steps 

```{r}
grViz("
digraph flowchart {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]



  # RAW 'NODE' STATEMENTS 
  node [shape = box,
        fontname = Helvetica]
  'GSE13937_series_matrix.txt'; 'A-GEOD-8835.adf.txt'; 'A-GEOD-8835_comments.txt';
  
  
  # LOAD 'NODE' STATEMENTS 
  node [shape = box,
        fontname = Helvetica]
  
  raw_data ; 'data_load.csv'
  'raw_probes'; 'raw_comments'; 'probes_data_load.csv'
  
  
  # CLEAN 'NODE' STATEMENTS 
  node [shape = box,
        fontname = Helvetica]
  
  'data_clean.csv' 
  'probes_data_clean.csv'
  
  # AUGMENT 'NODE' STATEMENTS
  node [shape = box,
        fontname = Helvetica]
  
  data_aug
  'data_aug_wide.csv'
  'data_aug_long.csv'
  
  # RESULTS
  node [shape = box,
        fontname = Helvetica]
  'Results and visualizations' 
  
  # 'EDGE' STATEMENTS 
  #Raw - load
  'GSE13937_series_matrix.txt' -> raw_data -> 'data_load.csv'
  'A-GEOD-8835.adf.txt' -> 'raw_probes'
  'A-GEOD-8835_comments.txt' -> 'raw_comments'
  {'raw_probes' 'raw_comments'} -> 'probes_data_load.csv'
  
  #Load - clean
  'data_load.csv' -> 'data_clean.csv'
  'probes_data_load.csv' -> 'probes_data_clean.csv'
  
  #Clean - augmented
  'data_clean.csv' -> data_aug
  {data_aug 'probes_data_clean.csv'} -> 'data_aug_long.csv'
  'data_aug_long.csv' -> 'data_aug_wide.csv'
  'data_aug_wide.csv' -> 'data_aug_long.csv'



 #Augmented - Visualizations 
{'data_aug_wide.csv' 'data_aug_long.csv'} -> 'Results and visualizations' 
 
  
{ rank = same; 'GSE13937_series_matrix.txt'; 'A-GEOD-8835.adf.txt'; 'A-GEOD-8835_comments.txt' }
{ rank = same; 'data_clean.csv'; 'probes_data_clean.csv' }


}
")
```


```{r}
graph <-
  create_graph() %>%
  add_path(
    n = 3,
    type = "path",
    edge_aes = edge_aes(
      style = "dot",
      color = c("red", "blue")))

# View the graph's internal
# node data frame; the node
# aesthetic attributes have
# been inserted
graph %>%
  get_edge_df()
```


## Results
```{r cars, echo = TRUE}
summary(cars)
```

## Results

## Results

## Results

## Discussion
```{r pressure}
plot(pressure)
```

## Discussion


