---
title: "Group 11 presentation"
# subtitle: "MiRNA expression in squamous cell carcinoma and adenocarcinoma of the esophagus and associations with survival"
author: "Dalsberg Jørgensen, Jonas; Gutierrez Leon, Alvaro; Hoang Viet Minh Pham, Jake; Romero Yianni, Daniel"
date: "5/7/2022"
output: ioslides_presentation
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Introduction
- **Dataset source:** MiRNA expression in squamous cell carcinoma and adenocarcinoma of the esophagus and associations with survival.

- **Objective of the project:** To reproduce the findings of the authors and elaborate on their visualizations.

- Bullet 3

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Materials and Methods

- Bullet 1
- Bullet 2
- Bullet 3

## Materials and Methods

## Results
```{r cars, echo = TRUE}
summary(cars)
```

## Results

## Results

## Results

## Discussion
```{r pressure}
plot(pressure)
```

## Discussion


