---
title: "Group 11 presentation"
# subtitle: "MiRNA expression in squamous cell carcinoma and adenocarcinoma of the esophagus and associations with survival"
author: "Dalsberg Jørgensen, Jonas; Gutierrez Leon, Alvaro; Hoang Viet Minh Pham, Jake; Romero Yianni, Daniel"
date: "5/7/2022"
output: 
  ioslides_presentation: 
    font-family: 'Helvetica'
    #widescreen: true
    #smaller: true
---
<style type="text/css">
body p {
  color: #000000;
}
</style>



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(DiagrammeR)
```

## Introduction
- **Dataset source:** MiRNA expression in squamous cell carcinoma and adenocarcinoma of the esophagus and associations with survival.

<br>

- **Objective of the project:** To reproduce the findings of the authors and elaborate on their visualizations.

## Materials and Methods
### Patient data: 
- **GSE13937_series_matrix.txt**
<br>

- National Center for Biotechnology Information website   (https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE13937)

<br>

### Microarray information:
- **A-GEOD-8835.adf.txt** and **A-GEOD-8835_comments.txt** 

- European Bioinformatics Institute website (https://www.ebi.ac.uk/arrayexpress/arrays/A-GEOD-8835/)  


## Materials and Methods
### Flowchart of the wrangling steps 




## Results
```{r cars, echo = TRUE}
summary(cars)
```

## Results

## Results

## Results

## Discussion
```{r pressure}
plot(pressure)
```

## Discussion

```{r}
grViz("
digraph boxes_and_circles {

  # a 'graph' statement
  graph [overlap = true, fontsize = 10]

  # several 'node' statements
  node [shape = box,
        fontname = Helvetica]
  A; B; C; D; E; F

  node [shape = circle,
        fixedsize = true,
        width = 0.9] // sets as circles
  1; 2; 3; 4; 5; 6; 7; 8

  # several 'edge' statements
  A->1 B->2 B->3 B->4 C->A
  1->D E->A 2->4 1->5 1->F
  E->6 4->6 5->7 6->7 3->8
}

")
```


